Age-related changes in plant growth and traits

### 2015-08-05 results_accessory_v3.Rmd
continuing to clean up little bits of analyses
found several little mistakes...

```{r, echo=FALSE,results='hide', message=FALSE}
library(remake)
create_bindings()

@@

##Summary of outcomes
1. Total reproductive investment is by far the best correlate with total plant size (or growth investment)
2. Plants with smaller seeds, smaller adult sizes, and higher seedset have lower accessory costs. It is mathematically plausable that the concept of "accessory costs" is not all that different from "seed set"
  * In other words, plants with higher seed set, have lower accessory costs due to calculations
  * It is nice to have a data set that shows, across 14 species, that larger plants have lower seed set.
3. Bigger plants have higher RA. 
  * Plants that produce more buds, invest more absolute energy into either pre-pollination tissues or propagules also have higher RA.
  * As plants get bigger, there is a slight shift of energy from pre-pollination tissues to propagules, but this is a small effect 
  *(i.e. accessory costs decline slightly with increasing plant size)
4. Among reproducing individuals, bigger or older plants DO NOT have higher seedset, although more individuals become reproductively mature over time. 
  * Proportional pre-pollination costs also decrease with plant age in most species
5. Species differ enormously in their relative investment in different reproductive tissue types

@@

##Which measure of reproductive output best correlates with plant size or growth (growth plotted here)
* Measuring total reproductive output has a much stronger correlation than investment in fruit weight or propagules
* To demonstrate the point that most investment is in prepollination tissues, the regression of total weight against prepollination investment is as good as total reproductive investment - one could just count buds + flowers!
* Note that each of these figures (and models) only includes individuals with non-zero investment in the reproductive pool of interest

@@

mod <- lm (log(total_weight)~log(prepollen_all_inv), data=subset(SummaryInd,prepollen_all_inv>0))
plot(prepollen_all_inv~total_weight,data=subset(SummaryInd,prepollen_all_inv>0), log="xy",col=col.spp[as.factor(species)], pch=16, xlab="", ylab="prepollen investment (mg)", xlim=c(100,2000000))
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)
```

##How do accessory costs shift with seed size?

### Comparing "per successful seed" and "proportion reproductive investment" accessory cost calculations 
  - calculating accessory costs on a per seed basis stratify the data much more by species 
  - cross-species variation is accentuated in plots calculated as "per successful seed" (vs. those with proportional accessory costs), because the species that have more seeds (lower proportional accessory costs), also have higher seedset

    - Larger-seeded species have higher accessory costs, as has been shown in other studies
    - However, it is also true that "larger species" and species with lower seed set have higher accessory costs
    - And that species with greater prepollination investment have higher accessory costs (since this is nearly the complement to propagule investment)

- Taken together these data (and various other plots, not shown) suggest that accessory costs (as a proportion) are most strongly driven by seedset
- In other words, if flowers are pollinated and develop into mature seeds, the plants ends up investing more energy in reproduction and that extra energy is being invested into propagules.
- Therefore, seed set goes up and by default, a greater proportion of energy goes into propagules and less into "accessory costs"

```{r, echo=FALSE,message=FALSE,warning=FALSE,fig.width=12, fig.height=6}
options(scipen=999)
par(mfrow=c(1,2), cex=1, omi=c(0.4,0.6,0.7,0.3), mai=c(.7,1,0.3,0.3))

#mod <- lm(log(seed_size)~log(accessory_per_seed),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0))
mod <- lm(log(seed_size)~(accessory_per_seed_mean),SummarySpp)
plot(accessory_per_seed~seed_size,SummaryInd, log="xy", pch=16,col=col.spp[as.factor(species)],ylab="accessory costs per successful seed",xlab="",cex=.9)
points((accessory_per_seed_mean)~seed_size,SummarySpp, pch=16,col=col.spp[as.factor(species)],cex=1.8)
words.bottom.right.logxy(mod)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

@@

* Bigger seeds have bigger fixed costs of making that seed (1st plot)
* But other than LEES having much lower costs, no shifts across species in their relative costs to make a seed (2nd plot); and LEES is one of the species where I use "propagule" not a single seed, so its "seed size" is higher and "accessory costs" slightly lower, since all fruit parts are part of the propagule 
* In other words, patterns of accessory costs vs. seed size, plant size, etc come about due to the differential effect of bud, flower abortion across species  
```{r, echo=FALSE,message=FALSE,warning=FALSE,fig.width=12, fig.height=6}
par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))
plot(seed_size~seedcosts,data=subset(SummarySpp),log="xy",pch=16,col=col.spp[as.factor(species)],xlab="costs to make 1 seed (mg)",cex=1.2)
mod <- lm(seedcosts~seed_size, SummarySpp)
words.bottom.right.logxy(mod)
text(seed_size~seedcosts,data=subset(SummarySpp),labels=species, pos=1,offset=.6,cex=0.8,col="black")

@@

###Seedset by age
* Replotting the seedset data by age, showing that the correlation between seedset and accessory costs is not primarily age related
* At most, there are most "old" plants with very low seedset 
```{r, echo=FALSE,message=FALSE,fig.width=6, fig.height=6}
par(mfrow=c(1,1), cex=1, omi=c(0.6,0.3,0.3,0.3), mai=c(0.8,1,0.3,0.3))

mod <- lm(log(seedset)~log(prop_propagule),data=subset(SummaryInd,seedset>0&seedset<1))
plot(prop_propagule~seedset,data=subset(SummaryInd,seedset>0&seedset<1), log="xy", pch=16,col=col.age[as.factor(age)],ylab="proportion reproduction to propagules (1-accessory)",xlab="")
words.bottom.right.logxy(mod)
legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
mtext("Seed set",1, outer=TRUE,cex=1.1)
```

@@

mod <- lm(log(ReproInv)~log(prop_propagule),data=subset(SummaryInd,prop_propagule>0))
plot(prop_propagule~ReproInv,data=subset(SummaryInd,prop_propagule>0), log="xy", pch=16,col=col.spp[as.factor(species)],xlab="",ylab="Propagules (as proportion repro inv)")
words.top.right.logxy(mod)
mtext("Reproductive investment (mg)",1, outer=TRUE,cex=1.1)
```

@@

* RA is also correlated with count of floral units - the total number of buds produced (i.e. final development stage can be buds, flowers, aborted fruit or fruit)
* This is true for many individual species as well as across species
* RA and seed count are also correlated, but mainly that no low RA individuals have high seed counts
```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(0.6,0.3,0.1,0.3), mai=c(0.8,1,0.3,0.3))  
mod <- lm(log(RA)~log(repro_all_count),data=subset(SummaryInd,repro_all_count>0))
plot(repro_all_count~RA,data=subset(SummaryInd,repro_all_count>0),col=col.spp[as.factor(species)],pch=16,log="xy",ylab="# of buds produced",xlab="")
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)

mod <- lm(log(RA)~log(seed_count+.1),data=subset(SummaryInd,repro_all_count>0))
plot((.1+seed_count)~RA,data=subset(SummaryInd,repro_all_count>0),col=col.spp[as.factor(species)],pch=16,log="xy",ylab="# of seeds produced",xlab="")
words.bottom.right.logxy(mod)
mtext("RA",1, outer=TRUE,cex=1.1)

yvar <- "repro_all_count"
xvar <- "RA"

data <- subset(SummaryInd, repro_all_count>0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm((log(x[[yvar]])) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

@@

@@

* If they shifted their proportional investment, there would be a relationship between RA and the proportional investment in 1 (or more) of the 5 reproductive energy pools. If they do not shift their proportional investment, all 5 would have no relationship.
    ** Only "proportional energy to pre-pollination aborted tissues" shows a significant decline with increasing RA - and it has a very convincing decline. Since no other pool shows an increase in proportional investment, that extra energy must be distributed fairly randomly across other pools

* Simultaneously, all tissue pools should show a positive relationship between actual investment amounts (mg) and RA
  ** Indeed, all pools increase with increasing RA, although only "pre-pollination successful tissues" and "energy to propagules" have a convincing r-squared value (across all species)

* 
* It might be interesting to look at this pattern by species

@@

###Shifts across age
* Seedset shows a slight decrease with proportional plant height (the best proxy for "relative size")  
* this pattern likely exists because species that begin reproducing at shorter proportional heights have higher seedset  
* only LEES shows a significant decline with age, although most species have a segative slope  
* there is a similar pattern for Propagule investment (not shown)  
* Table shows results, by species, for seedset by proportional height  
```{r, echo=FALSE,message=FALSE}
par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))  
mod <- lm((prop_maxH)~asin(sqrt(seedset)),data=subset(SummaryInd,seedset<1&seedset>0))
plot(asin(sqrt(seedset))~prop_maxH,data=subset(SummaryInd,seedset<1&seedset>0), pch=16,col=col.spp[as.factor(species)])
words.top.right(mod)
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

@@

* Results, by species, for seedset by age  
* Only HEPU, LEES show significant decline, but again mostly negative slopes
```{r, echo=FALSE,message=FALSE}
yvar <- "seedset"
xvar <- "age"

data <- subset(SummaryInd, seedset>0&seedset<1)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

* A number of species show declines in accessory costs with age, but this effect disappears once you include only individuals that set *any* seed
```{r, echo=FALSE,message=FALSE}
yvar <- "prop_accessory"
xvar <- "age"

data <- subset(SummaryInd)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

* 8 of the 14 species show declines in allocation to pre-pollination tissues with increasing age
```{r, echo=FALSE,message=FALSE}
yvar <- "prop_prepollen_all"
xvar <- "age"

data <- subset(SummaryInd)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

@@

#Shifts in accessory costs across species and ages
##Overall results
- Accessory costs higher for bigger seeds

- Accessory costs higher for bigger species; these are the same species that invest less in RA

- Of course there is also a correlation between seed size and plant size, but actually not as strong as the accessory cost one, presumably because older plants have lower accessory costs as well as species that are inherently bigger

>>>>

```{r, echo=FALSE,results='hide', message=FALSE,warning=FALSE}
library(remake)
create_bindings()

@@

##Summary of outcomes
1. Total reproductive investment is the best correlate with total plant size (or growth investment)
2. Plants with smaller seeds, smaller adult sizes, and higher seedset have lower accessory costs. It is mathematically plausable that the concept of "accessory costs" is not all that different from "seed set"
    * In other words, plants with higher seed set, have lower accessory costs due to calculations
    * Across  the 14 species, plants with larger adult size have lower seed set.
3. Bigger plants have higher RA. 
    * Plants that produce more buds, invest more absolute energy into either pre-pollination tissues or propagules also have higher RA.
    * As plants get bigger, there is a slight shift of energy from pre-pollination tissues to propagules, but this is a small effect 
    *(i.e. accessory costs decline slightly with increasing plant size)
4. Among reproducing individuals, bigger or older plants DO NOT have higher seedset, although more individuals become reproductively mature over time. 
    * Proportional pre-pollination costs also decrease with plant age in most species
5. Species differ enormously in their relative investment in different reproductive tissue types

@@

##Which measure of reproductive output best correlates with plant size or growth
* Measuring total reproductive output has a much stronger correlation than investment in fruit weight or propagules
* The regression of total weight against prepollination investment is as good as total reproductive investment - one could just count buds + flowers!
    * This is likely because prepollination investment is much a large proportion of total reproductive investment
* Note that each of these figures (and models) only includes individuals with non-zero investment in the reproductive pool plotted

@@

mod <- lm (log(total_weight)~log(prepollen_all_inv), data=subset(SummaryInd,prepollen_all_inv>0))
plot(prepollen_all_inv~total_weight,data=subset(SummaryInd,prepollen_all_inv>0), log="xy",col=col.spp[as.factor(species)], pch=16, xlab="", ylab="prepollen investment (mg)", xlim=c(100,2000000))
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)

mtext("Total plant size (mg)",1, outer=TRUE,cex=1.2)
```

### Comparing accessory cost calculations expressed as "per successful seed" versus "proportion reproductive investment"  
  - The difference between the two calculations is seed count
  - calculating accessory costs on a per seed basis stratify the data much more by species 
      * this is because the species that have more seeds (lower proportional accessory costs), also have higher seedset
  - Calculations per seed tell you energy input relative to fecundity
```{r, echo=FALSE,message=FALSE,warning=FALSE,fig.width=14, fig.height=7}
options(scipen=10)
par(mfrow=c(1,2), cex=1, omi=c(0.4,0.6,0.7,0.3), mai=c(1.1,1,0.3,0.3)) 
mod <- lm(log(seed_count)~species*accessory_per_seed,data=subset(SummaryInd,seed_count>0))
plot(seed_count~accessory_per_seed,SummaryInd, log="xy", pch=16,col=col.spp[as.factor(species)],ylab="seed count",xlab="accessory costs per successful seed (mg)",cex=.9)
words.bottom.left.logxy(mod)

plot(seed_count~asin(sqrt(prop_accessory)),SummaryInd, log="y", pch=16,col=col.spp[as.factor(species)],ylab="",xlab="proportion of reproduction to accessory tissues (asin)",cex=.9)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
```
###Do accessory costs shift with seed size?
    * These plots presented using both accessory cost calculations

Results:  
    - Larger-seeded species have higher accessory costs, as has been shown in other studies  
    - Also: "larger species" and species with lower seed set have higher accessory costs  
    - And: species with greater prepollination investment have higher accessory costs (since this is the majority of accessory costs for most species)  
    - When all 4 variables put into a single model, regardless of "accessory cost" calculation, seedset always by far the most significant correlate   
        * seed size is least frequently a correlate in models, although of course highly significant when analyzed on its own

Interpretation:  
    - Not sure one can separate the effect of plant size, seed set, seed size on what drive accessory costs  
    - the reason seed set is strongly correlated, is because if flowers are pollinated and develop into mature seeds, the individual plant ends up investing more energy in reproduction and that extra energy is being invested into propagules, reducing accessory costs.   
        * This is true at the species and individual level.

mod <- lm(log(accessory_per_seed)~(seedset)*log(prepollen_all_inv)*log(total_weight)*log(seed_size),data=subset(SummaryInd,seedset>0&prepollen_all_per_seed>0))
summary(mod)

```{r, echo=FALSE,message=FALSE,warning=FALSE,fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(0.4,0.6,0.7,0.3), mai=c(.7,1,0.3,0.3))
#mod <- lm(log(seed_size)~log(accessory_per_seed),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0))
mod <- lm(log(seed_size)~(accessory_per_seed_mean),SummarySpp)
plot(accessory_per_seed~seed_size,SummaryInd, log="xy", pch=16,col=col.spp[as.factor(species)],ylab="accessory costs per successful seed",xlab="",cex=.9)
points((accessory_per_seed_mean)~seed_size,SummarySpp, pch=16,col=col.spp[as.factor(species)],cex=1.8)
words.bottom.right.logxy(mod)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

@@

* Bigger seeds have bigger fixed costs of making that seed (1st plot)
* But other than LEES having much lower costs, no shifts across species in their relative costs to make a seed (2nd plot); and LEES is one of the species where I use "propagule" not a single seed, so its "seed size" is higher and "accessory costs" slightly lower, since all fruit parts are part of the propagule 
* In other words, patterns of accessory costs vs. seed size, plant size, etc come about due to the differential effect of bud, flower abortion across species  
```{r, echo=FALSE,message=FALSE,warning=FALSE,fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))
plot(seed_size~seedcosts,data=subset(SummarySpp),log="xy",pch=16,col=col.spp[as.factor(species)],xlab="costs to make 1 seed (mg)",cex=1.2)
mod <- lm(seedcosts~seed_size, SummarySpp)
words.bottom.right.logxy(mod)
text(seed_size~seedcosts,data=subset(SummarySpp),labels=species, pos=1,offset=.6,cex=0.8,col="black")

@@

###Seedset,seed count by age, size, RA
* Replotting the seedset data by age, showing that the correlation between seedset and accessory costs is not age related
* At most, there are most "old" plants with very low seedset  
* these plots only include individuals with some seedset, thereby ignoring most young plants

```{r, echo=FALSE,message=FALSE,fig.width=7, fig.height=7}
par(mfrow=c(1,1), cex=1, omi=c(0.2,0.3,0.3,0.3), mai=c(1.1,1,0.3,0.3))

mod <- lm(log(seedset)~log(prop_propagule),data=subset(SummaryInd,seedset>0&seedset<1))
plot(prop_propagule~seedset,data=subset(SummaryInd,seedset>0&seedset<1), log="xy", pch=16,col=col.age[as.factor(age)],ylab="proportion RE to propagules (1-accessory)",xlab="seed set")
words.bottom.right.logxy(mod)
legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
```

* There is no overall shift in either seedset or proportional allocation to propagules with increasing RA  
```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7,warning=FALSE}
par(mfrow=c(1,2), cex=1, omi=c(0.2,0.3,0.3,0.3), mai=c(1.1,1,0.3,0.3)) 
mod <- lm(asin(sqrt(seedset))~asin(sqrt(RA)),data=subset(SummaryInd,seedset>0&seedset<1))
plot(asin(sqrt(RA))~asin(sqrt(seedset)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp[as.factor(species)])
words.bottom.right(mod)

mod <- lm(asin(sqrt(prop_propagule))~asin(sqrt(RA)),data=subset(SummaryInd,prop_propagule>0))
plot(asin(sqrt(RA))~asin(sqrt(prop_propagule)),data=subset(SummaryInd,seedset>0&seedset<1), log="x", pch=16,col=col.spp[as.factor(species)])
words.bottom.right.logx(mod)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
```

* Furthermore, looking within species  
    - Not a single species shows an increase in prop_propagule with increasing RA  
    - And for seedset vs RA, only HATE shows an increase, and HEPU a decrease  
    - So no, there are no compounding benefits to increasing RA

```{r, echo=FALSE,message=FALSE,fig.width=7, fig.height=7,warning=FALSE}
yvar <- "RA_asin"
xvar <- "seedset"

data <- subset(SummaryInd,seedset>0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(x[[yvar]] ~  asin(sqrt(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

* And there are absolutely no patterns of interest relative to seed count   
    * it doesn't even correlate very well with RA or plant size

@@

options(scipen=5)
mod <- aov(log(ReproInv)~species*log(prop_propagule),data=subset(SummaryInd,prop_propagule>0))
summary(mod)

options(scipen=20)
mod <- lm(log(ReproInv)~species*log(prop_propagule),data=subset(SummaryInd,prop_propagule>0))
plot(prop_propagule~ReproInv,data=subset(SummaryInd,prop_propagule>0), log="xy", pch=16,col=col.spp[as.factor(species)],xlab="",ylab="Propagules (as proportion repro inv)")
words.top.right.logxy(mod)
mtext("Reproductive investment (mg)",1, outer=TRUE,cex=1.1)
```

@@

* RA is also correlated with count of floral units - the total number of buds produced (i.e. final development stage can be buds, flowers, aborted fruit or fruit)
* This is true for many individual species as well as across species

```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(0.6,0.3,0.1,0.3), mai=c(0.8,1,0.3,0.3))  
mod <- lm(log(RA)~log(repro_all_count),data=subset(SummaryInd,repro_all_count>0))
plot(repro_all_count~RA,data=subset(SummaryInd,repro_all_count>0),col=col.spp[as.factor(species)],pch=16,log="xy",ylab="# of buds produced",xlab="")
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)
mtext("RA",1, outer=TRUE,cex=1.1)
```

```{r, echo=FALSE,message=FALSE,fig.width=28, fig.height=28}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "repro_all_count"
xvar <- "RA_asin"

data <- subset(SummaryInd, repro_all_count>0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm((log(x[[yvar]])) ~  (x[[xvar]])))
results <- summarise_all_fits(lmfits)

@@

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",
                    main=spp)
    }
```

@@

* If they shifted their proportional investment, there would be a relationship between RA and the proportional investment in 1 (or more) of the 5 reproductive energy pools. If they do not shift their proportional investment, all 5 would have no relationship.  
      * Only "proportional energy to pre-pollination aborted tissues" shows a significant decline with increasing RA - and it has a very convincing decline.   
      * Since no other pool shows an increase in proportional investment, that extra energy must be distributed fairly randomly across other pools

* Simultaneously, all tissue pools should show a positive relationship between actual investment amounts (mg) and RA  
      * However, only "pre-pollination successful tissues" and "energy to propagules" have a convincing r-squared value (across all species)

* It might be interesting to look at this pattern by species

@@

###Shifts across age and height
* Seedset shows a slight decrease with proportional plant height (the best proxy for "relative size")  
    * this pattern likely exists because species that begin reproducing at shorter proportional heights have higher seedset  
    * only LEES shows a significant decline

* the same analysis can be done on seedset by age, with similar response    
    * Only HEPU, LEES show significant decline

yvar <- "seedset"
xvar <- "prop_maxH""
```{r, echo=FALSE,message=FALSE}
par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))  
mod <- lm((prop_maxH)~asin(sqrt(seedset)),data=subset(SummaryInd,seedset<1&seedset>0))
plot(asin(sqrt(seedset))~prop_maxH,data=subset(SummaryInd,seedset<1&seedset>0), pch=16,col=col.spp[as.factor(species)])
words.top.right(mod)
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

@@

yvar <- "prop_propagule"
xvar <- "total_weight"

* Only EPMI shows a decline in prop propagule with increasing plant weight  
* No species show an increase in prop propagule with increasing plant weight  
* Of course the proportion of species with prop propagule > 0 increases with plant size

```{r, echo=FALSE,message=FALSE}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "prop_propagule"
xvar <- "total_weight"

data <- subset(SummaryInd,prop_propagule>0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

@@

#Shifts in accessory costs across species and ages
##Overall results
- Of course there is also a correlation between seed size and plant size, but actually not as strong as the accessory cost one, presumably because older plants have lower accessory costs as well as species that are inherently bigger

### 2015-08-05 results_growth_short.Rmd
continuing to clean up little bits of analyses
found several little mistakes...

###Plants that allocate more to reproduction (higher RA) have a lower RGR
- When looked at individually, this pattern holds for all species except PEPU and PELA, although there is lots of variation in the exact trade-off pattern displayed by different species  
- You can also look at the plots of RGR vs RA and identify the RA at which RGR is impacted. Some plots show a very linear decline throught, whereas for others there is a distinct "knickpoint" -i.e. BOLE, EPMI, HATE   
- More robust curve-fitting techniques are required to better illustrate this pattern (**CURVE FITTING**)

```{r, echo=FALSE,message=FALSE}
par(mfrow=c(2,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2)) 
mod <- lm(RGR~asin(sqrt(RA)),data=subset(SummaryInd,RA>0))
plot((RA+.01)~RGR, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.top.right.logxy(mod)

@@

mod <- lm(log(growth_stem_area)~asin(sqrt(RA)),data=subset(SummaryInd,RA>0))
plot((RA+.01)~growth_stem_area, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.top.right.logxy(mod)

@@

mod <- lm(log(prop_growth_height)~asin(sqrt(RA)),data=subset(SummaryInd,growth_height>0&species!="PEPU"&species!="PELA"&species!="COER"))
plot((RA+.01)~(prop_growth_height), data=subset(SummaryInd,species!="PEPU"&species!="PELA"), log="xy", col=col.spp[as.factor(species)],pch=16)

legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.top.right.logxy(mod)

mod <- lm(log(growth_height)~asin(sqrt(RA)),data=subset(SummaryInd,RA>0&growth_height>0))
plot((RA+.01)~(growth_height), SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
```

###PCA analysis indicates the same two patterns
* This combination of variables shows that RGR is approximately opposite a collection of variables that indicate a plant is "bigger" - so smaller plants have higher RGR
* Orthoganal to these in WD vs. maxH, LMA_mean, seed_size, and shoot_growth - species that are taller as adults have bigger seeds, higher LMA, and greater shoot growth (both stem growth & leaf count), independent of their current (age dependent) size
* I interpret this to mean that the three traits (Hmax, LMA, WD) strongly influence each other - presumably, Hmax a function of WD and LMA), but do not particularly 
* this analysis doesn't include accessory proportions, because then I have to use subset of reproducing individuals, greatly reducing sample size. Including these variables, doesn't change the basic story.
* fine tuning:  
  ** remove RGR leaf (similar to RGR)
  ** remove prop_max_weight and prop_max_repro (similar to prop_maxH)

>>>>

###Plants that allocate more to reproduction (higher RA) have lower growth
- When looked at individually, this pattern holds for most species, although there is lots of variation in the exact trade-off pattern displayed by different species  
    * when plotted again stem diameter increment, most species show a distinctly linear pattern - decline in stem diameter increment fairly exactly offset by increases in RA across all individuals of the species   
    * for plots of RGR vs RA some species have a distinct "knickpoint" where growth impacted -i.e. BOLE, EPMI, HATE

```{r, echo=FALSE,message=FALSE, warning=FALSE}
par(mfrow=c(2,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2)) 
mod <- lm(RGR~asin(sqrt(RA)),data=subset(SummaryInd,RA>0))
plot((RA+.01)~RGR, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.top.right.logxy(mod)

@@

mod <- lm(log(prop_growth_stem_diam)~asin(sqrt(RA)),data=subset(SummaryInd,RA>0))
plot((RA+.01)~prop_growth_stem_diam, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.top.right.logxy(mod)

@@

mod <- lm(log(prop_growth_height)~asin(sqrt(RA)),data=subset(SummaryInd,growth_height>0&species!="PEPU"&species!="PELA"&species!="COER"))
plot((RA+.01)~(prop_growth_height), data=subset(SummaryInd,species!="PEPU"&species!="PELA"), log="xy", col=col.spp[as.factor(species)],pch=16)
```

```{r, echo=FALSE,message=FALSE, warning=FALSE}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "growth_stem_diam"
xvar <- "RA"

data <- subset(SummaryInd,RA>0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  asin(sqrt(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",
                    main=spp)
    }

mtext("RA", 1, outer=TRUE,cex=1.2)
mtext("Yearly increase in stem diameter (mm)", 2, outer=TRUE,cex=1.2)
```
###PCA analysis indicates the same two patterns
* This combination of variables shows that RGR is approximately opposite a collection of variables that indicate a plant is "bigger" - so smaller plants have higher RGR
* Orthoganal to these in WD vs. maxH, LMA_mean, seed_size, and shoot_growth - species that are taller as adults have bigger seeds, higher LMA, and greater shoot growth (both stem growth & leaf count), independent of their current (age dependent) size
* I interpret this to mean that the three traits (Hmax, LMA, WD) strongly influence each other - presumably, Hmax a function of WD and LMA), but do not particularly 
* this analysis doesn't include accessory proportions, because then I have to use subset of reproducing individuals, greatly reducing sample size. Including these variables, doesn't change the basic story.
* fine tuning:  
  ** remove RGR leaf (similar to RGR)
  ** remove prop_max_weight and prop_max_repro (similar to prop_maxH)
